---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# kader

The goal of kader is to supply functions to compute nonparametric kernel estimators for  

* density estimation using a data-adjusted kernel or an
appropriate rank-transformation, and for  
* regression using a data-adjusted kernel.  

The functions are based on the theory introduced in  

* Srihera, R., Stute, W. (2011): Kernel adjusted density estimation.
Statistics and Probability Letters 81, 571 - 579,
URL http://dx.doi.org/10.1016/j.spl.2011.01.013.  
* Eichner, G., Stute, W. (2012): Kernel adjusted nonparametric regression.
Journal of Statistical Planning and Inference 142, 2537 - 2544,
URL http://dx.doi.org/10.1016/j.jspi.2012.03.011.  
* Eichner, G., Stute, W. (2013): Rank Transformations in Kernel Density
Estimation. Journal of Nonparametric Statistics 25(2), 427 - 445,
URL http://dx.doi.org/10.1080/10485252.2012.760737.  

A very brief summary of the theory and sort of a vignette is presented in
Eichner, G. (2017): Kader - An R package for nonparametric kernel adjusted
density estimation and regression. In: Ferger, D., et al. (eds.): From
Statistics to Mathematical Finance, Festschrift in Honour of Winfried Stute.
Springer International Publishing. To appear in Oct. 2017.


## Installation

You can install kader from CRAN with:

```{r cran-installation, eval = FALSE}
install.packages("kader")
```

or from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("GerritEichner/kader")
```

## Example

This example shows you how to estimate at $x_0 = 2$ the value of the density 
function of the probability distribution underlying Old-Faithful's eruptions data
using the (nonrobust) method of Srihera & Stute (2011). The initial grid 
(given to `Sigma`) on which the minimization of the estimated MSE as a function
of a (kernel-adjusting) scale parameter $\sigma$ is started is rather coarse here
to save computing time.

```{r example}
library(kader)
x0 <- 2
sigma <- seq(0.01, 10, length = 21)
fit <- kade(x = x0, data = faithful$eruptions, method = "nonrobust",
  Sigma = sigma, ticker = TRUE)
print(fit)
```
